---
title: "Vale Stock work"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning = FALSE, include = FALSE, error = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(cowplot)
library(ggthemes)
library(latticeExtra)
```

```{r}
library(readxl)
ValeStockPrice <- read_excel("~/Desktop/Vale Stock Prices/ValeStockPrice.xlsx", 
    sheet = "Vale v Fortescue")
#View(ValeStockPrice)
```

```{r}
#ValeStockPrice %>%  
    #as.data.frame()
```

```{r}
(Valev62 = ValeStockPrice %>% 
  select(Vale_Close,`62_Fe`) %>% 
  ggplot(aes(x = `62_Fe`, y = Vale_Close)) +
  geom_point()+
  xlab('Iron Ore Fines 62% Fe') +
  ylab('Vale Close'))

(FMXv62 = ValeStockPrice %>% 
  select(FMX_Close, `62_Fe`) %>% 
  ggplot(aes(x =`62_Fe`, y = FMX_Close)) + 
  geom_point() +
  xlab('Iron Ore Fines 62% Fe') +
  ylab('FMX Close')  )

  
```

```{r}
LastyearStocks = ValeStockPrice %>%
  filter(Date >= as.Date("2018-08-02"))
  
```


```{r}
(Valev62_2019 = LastyearStocks %>% 
  select(Vale_Close,`62_Fe`) %>% 
  ggplot(aes(x = `62_Fe`, y = Vale_Close)) +
  geom_point()+
  xlab('Iron Ore Fines 62% Fe') +
  ylab('Vale Close')+
  ggtitle('Vale Price Aug 2018 - Aug 2019'))

(FMXv62_2019 = LastyearStocks %>% 
  select(FMX_Close, `62_Fe`) %>% 
  ggplot(aes(x =`62_Fe`, y = FMX_Close)) + 
  geom_point() +
  xlab('Iron Ore Fines 62% Fe') +
  ylab('FMX Close')+
  ggtitle('FMX Price Aug 2018 - Aug 2019'))

```

```{r, warning = FALSE}
(Valev58 = ValeStockPrice %>% 
  select(Vale_Close,`58_Fe`) %>% 
  ggplot(aes(x = `58_Fe`, y = Vale_Close)) +
  geom_point()+
  xlab('Iron Ore Fines 58% Fe') +
  ylab('Vale Close'))

(FMXv58 = ValeStockPrice %>% 
  select(FMX_Close, `58_Fe`) %>% 
  ggplot(aes(x =`58_Fe`, y = FMX_Close)) +
  geom_point() +
  xlab('Iron Ore Fines 58% Fe') +
  ylab('FMX Close')  )
```


```{r, warning = FALSE}
(Valev58_2019 = LastyearStocks %>% 
  select(Vale_Close,`58_Fe`) %>% 
  ggplot(aes(x = `58_Fe`, y = Vale_Close)) +
  geom_point()+
  xlab('Iron Ore Fines 58% Fe') +
  ylab('Vale Close')+
  ggtitle('Fe58 Vale Price Aug 2018 - Aug 2019'))

(FMXv58_2019 = LastyearStocks %>% 
  select(FMX_Close, `58_Fe`) %>% 
  ggplot(aes(x =`58_Fe`, y = FMX_Close)) + 
  geom_point() +
  xlab('Iron Ore Fines 58% Fe') +
  ylab('FMX Close')+
  ggtitle('Fe 58 FMX Price Aug 2018 - Aug 2019'))
```

```{r, warning = FALSE}
#Looking at Vale stock price vs other commodity exposures (Nickel and Copper) since 2015.

(ValevCopper = ValeStockPrice %>% 
  select(Vale_Close, Cu_Price) %>% 
  ggplot(aes(x = Cu_Price, y = Vale_Close)) +
  geom_point()+
  xlab('Copper Price (USD/t)') +
  ylab('Vale Close')+
  ggtitle('Copper Price v. Vale Price'))

(ValevNickel = ValeStockPrice %>% 
  select(Vale_Close, Ni_Price) %>% 
  ggplot(aes(x = Ni_Price, y = Vale_Close)) +
  geom_point()+
  xlab('Nickel Price (USD/t)') +
  ylab('Vale Close')+
  ggtitle('Nickel Price v. Vale Price'))
```


``````{r, warning = FALSE}
#Looking at Vale stock price vs other commodity exposures (Nickel and Copper) since Aug 2018.

(ValevCopper_2019 = LastyearStocks %>% 
  select(Vale_Close, Cu_Price) %>% 
  ggplot(aes(x = Cu_Price, y = Vale_Close)) +
  geom_point()+
  xlab('Copper Price (USD/t)') +
  ylab('Vale Close')+
  ggtitle('Copper Price v. Vale Price Aug 2018 - Aug 2019'))

(ValevNickel_2019 = LastyearStocks%>% 
  select(Vale_Close, Ni_Price) %>% 
  ggplot(aes(x = Ni_Price, y = Vale_Close)) +
  geom_point()+
  xlab('Nickel Price (USD/t)') +
  ylab('Vale Close')+
  ggtitle('Nickel Price v. Vale Price Aug 2018 - Aug 2019'))

#In the last year - it does not suggest that copper or nickel prices have affected stock prices over the last year. It seems from the 2015-present graphs that there was a correlation between the commodity prices and vale stock. 
```


```{r, warning = FALSE}
#Looking at the stock prices of Vale and FMX against BRL and AUS exchange rate
(ValevBRL = ValeStockPrice %>% 
  select(Vale_Close, BRL_USDRate) %>% 
  ggplot(aes(x = BRL_USDRate, y = Vale_Close)) +
  geom_point()+
  xlab('BRL/USD exchange rate') +
  ylab('Vale Close')+
  ggtitle('Brazilian Real Exchange Rate v. Vale Price'))

(FMXvAUS = ValeStockPrice %>% 
  select(FMX_Close, AUS_USDRate) %>% 
  ggplot(aes(x = AUS_USDRate, y = FMX_Close)) +
  geom_point()+
  xlab('AUS/USD exchange rate') +
  ylab('FMX Close')+
  ggtitle('AUS Exchange Rate v. FMX Price'))

```

```{r, warning = FALSE}
#Looking at the stock prices of Vale and FMX against BRL and AUS exchange rate over the last year
(ValevBRL = LastyearStocks %>% 
  select(Vale_Close, BRL_USDRate) %>% 
  ggplot(aes(x = BRL_USDRate, y = Vale_Close)) +
  geom_point()+
  xlab('BRL/USD exchange rate') +
  ylab('Vale Close')+
  ggtitle('Brazilian Real Exchange Rate v. Vale Price Aug 2018 - Aug 2019'))

(FMXvAUS = LastyearStocks %>% 
  select(FMX_Close, AUS_USDRate) %>% 
  ggplot(aes(x = AUS_USDRate, y = FMX_Close)) +
  geom_point()+
  xlab('AUS/USD exchange rate') +
  ylab('FMX Close')+
  ggtitle('AUS Exchange Rate v. FMX Price Aug 2018 - Aug 2019'))

```

```{r}
graphValevBRL = LastyearStocks %>% 
  select(Date, Vale_Close, BRL_USDRate)

Graph1 = ggplot(data = graphValevBRL, aes(x = Date, y = BRL_USDRate)) +
  geom_line(size = 1, colour = 'blue')+
  xlab('Date') +
  ylab('Real/USD Exchange Rate')

Graph2 = ggplot(data = graphValevBRL , aes(x = Date, y = Vale_Close)) +
  geom_line(aes(x = Date, y = Vale_Close), size = 1, colour = 'dark green') +
  xlab('Date') +
  ylab('Vale Close') 

plot_grid(Graph1, Graph2, labels = c('Brazilian Real Exchange Rate', 'Vale Close'), label_size = 12)

#windows(xpinch=340, ypinch=340)

```


```{r}

graphFMXvAus = LastyearStocks %>% 
  select(Date, FMX_Close, AUS_USDRate)

Graph1a = ggplot(data = graphFMXvAus, aes(x = Date, y = AUS_USDRate)) +
  geom_line(size = 1, colour = 'blue')+
  xlab('Date') +
  ylab('AUS/USD Exchange Rate')

Graph2a = ggplot(data = graphFMXvAus , aes(x = Date, y = FMX_Close)) +
  geom_line(aes(x = Date, y = FMX_Close), size = 1, colour = 'dark green') +
  xlab('Date') +
  ylab('FMX Close') 

plot_grid(Graph1a, Graph2a, labels = c('AUS Exchange Rate', 'FMX Close'), label_size = 12)

#windows(xpinch=340, ypinch=340)
```


















